Entrainment of low Mach number thermals in stratified domains

### 2019-05-03 tex/stratified_thermals.tex
paper progress

\begin{figure*}[t!]
    \includegraphics[width=\columnwidth]{evolution_colormeshes.png}
    \caption{
    \label{fig:evolution_colormeshes} }
\end{figure*}

\subsection{Theoretical description of thermal evolution}
The evolution of thermals as buoyant vortex rings has been well described in
the unstratified, Boussinesq limit for decades (as early as e.g., CITE, and
see \citet{lecoanet&jeevanjee2018} for other sources). Buoyant motions 
in the atmospheres of stars and planets are generally large enough to feel the
atmospheric stratification, and therefore a more thorough tratment of the
evolution of thermals in stratified domains is required to understand the nature
of thermal entrainment in nature.

In this work, we focus on the non-dissipative, low Mach number regime, 
in which the ideal anelastic equations are a decent approximation to the fully
compressible equations. In this regime, the buoyancy is directly proportional to the
specific entropy. In the absence of diffusion, or in the limit where diffusivities
are sufficiently small, the volume-integrated total entropy is constant,
\begin{equation}
B \equiv \int_{\mathcal{V}} \rho\, s\, dV = \text{const},
\end{equation}
where $s = c_V \ln T - R \ln\rho$ is the specific entropy, with $c_V$ the
specific heat at constant volume and $R$ the ideal gas constant.

In a stratified domain, the hydrodynamic impulse is defined
\citet{shivamoggi2010},
\begin{equation}
\bm{I} = \frac{1}{2}\int_{\mathcal{V}} \bm{x}\times(\grad\times(\rho\bm{u}))dV,
\end{equation}
where $\bm{x}$ is the position vector, $\bm{u}$ is vector velocity, $\rho$ is density,
and $\mathcal{V}$ is the volume being integrated over. Furthermore, changes in the impulse
can be expressed
\begin{equation}
\frac{\partial\bm{I}}{\partial t} = \int_{\mathcal{V}}\frac{\partial}{\partial t}(\rho \bm{u})dV
= B\hat{z} + S,
\end{equation}
where $S$ is a combination of surface terms that disappears upon appropriate boundary conditions
on $\mathcal{V}$ \citep{shivamoggi2010}. As we have assumed that the buoyancy, $B$, is constant,
we can straightforwardly integrate
\begin{equation}
I_z = B t + I_0,
\end{equation}
for some constant $I_0$.

(need to work through this section carefully).
Assuming an adiabatically stratified atmosphere in
hydrostatic equilibrium, the vertical momentum equation is
\begin{equation}
 = - \partial_z \varpi +  g\frac{S_1}{c_P},
\label{eqn:buoyancy}
\end{equation}
where $w$ is vertical velocity, $S_1$ is specific entropy, $\varpi$ is the reduced pressure,
$D/Dt = \partial_t + (\bm{u}\cdot\grad)$ is the (eulerian? lagrangian?)
derivative, $g$ is gravity, and $c_P$ is the specific heat at constant pressure.
In the anelastic approximation, the density stratification is constant in time. 
OH GOD I DON'T KNOW THIS MATH WELL MAGIC MAGIC MAGIC.
By doing magic, we arrive at
\begin{equation}
P_z = \beta B t + P_0.
\end{equation}

Under the assumption that the thermal develops into a thin-core 
propagating vortex ring whose vortex core is radius $r$ away from the axis of symmetry, 
the impulse can be approximated as $I_z \approx \pi \rho r^2 \Gamma$, where 
$\Gamma$ is the circulation of the thermal vortex, which we assume to be constant. 
Rearranging, we find our first result,
\begin{equation}
r = \sqrt{\frac{B t + I_0}{\pi\rho\Gamma}}.
\label{eqn:r_theory}
\end{equation}
In the limit where $\rho \rightarrow \text{constant}$, as in the Boussinesq regime,
we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by
\citet{lecoanet&jeevanjee2018}. We find that the inclusion of stratification adds the
additional complexity of $r \propto \rho^{-1/2}$, such that downward-propogating 
vortex rings (as studied here) will not entrain to the same degree as boussinesq thermals,
and upward-propogating rings will entrain more.

We further assume that the volume-integrated momentum, $P_z \approx \rho V w_{th}$,
where $w_{th}$ is the vertical velocity of the thermal as a whole, and the volume
of the fluid region propogating with the thermal is a spheroid, $V = V_0 r^3$, for
some constant $V_0$. Plugging Eqn.~\ref{eqn:r_theory} into this approximation, we
find that
\begin{equation}
\rho^{-1/2}w = \left(\frac{(\pi\Gamma)^{3/2}}{V_0}\right)\frac{\beta B t + M_0}{(B t + I_0)^{3/2}}.
\end{equation}
Substituting $w = dz/dt$ and $\tau \equiv (Bt + I_0)/\Gamma$, We retrieve
\begin{equation}
\frac{dz}{\sqrt{\rho(z)}} 
= \left(\frac{\pi^{3/2}\Gamma}{V_0}\right)
\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
\label{eqn:general_theory}
\end{equation}
If the atmospheric stratification in which the thermal is falling is known, this
result can be straightforwardly integrated with $\rho(z)$ plugged in in order to
find the position of the thermal versus time. While we will leave this result
general for now, we will plug in our polytropic stratification at the end of
section \ref{sec:experiment}, and show that the resulting expression does a
good job of explaining the evolution of thermals in these atmospheres in
section \ref{sec:results}.

@@

\subsection{Anelastic Simulations}
In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic
thermals in cylindrical coordinates. 
We later verify that these simulations produce the same results a 3D fully compressible
simulations in 3D cartesian domains (see sec. REF). 
The LBR anelastic equations are \citep{lecoanet&all2014},
\begin{gather}
\td{\grad}\cdot\td{\bm{u}} = -\td{w}\partial_{\tilde{z}} \ln\rho_0 \\
\frac{D \td{\bm{u}}}{D \td{t}} = -\td{\grad} \td{\varpi} + g\frac{\td{S_1}}{c_P}\hat{z} + \frac{1}{\rho_0}\td{\grad}\cdot\left(\mu\td{\lilstressT}\right) \\
\frac{D \td{S_1}}{D\td{t}} = \frac{1}{\rho c_P}\td{\grad}\cdot\left(\kappa T_0 \td{\grad} \td{S_1}\right) + \frac{\mu}{\rho_0 T_0}\td{\sigma_{ij}}\partial_{\td{x_i}}\td{u_j}.
\end{gather}
where terms with tildes are dimensional, and where
$D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$. In our azimuthally symetric
domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have
no azimuthal velocity, $u_\phi$, we assume that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$. 
Under this approximation, the components of the stress tensor are
\begin{equation}
\begin{split}
&\td{\sigma}_{rr} = 2\frac{\partial \td{u_r}}{\partial \td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,
\td{\sigma}_{rz}     = \td{\sigma}_{zr} = \frac{\partial \td{w}}{\partial \td{r}} + \frac{\partial \td{u_r}}{\partial \td{z}}, \\
&\td{\sigma}_{\phi\phi} = 2\frac{\td{u_r}}{\td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,\,
\td{\sigma}_{r\phi}  = \td{\sigma}_{\phi r}  = 0, \\
&\td{\sigma}_{zz}       = 2\frac{\partial \td{w}}{\partial \td{z}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}}, \,\,\,\,\,\,
\td{\sigma}_{\phi z} = \td{\sigma}_{z \phi}  = 0,\qquad
\end{split}
\end{equation}
Furthermore, we assume that the dynamic viscosity, $\mu = \rho \nu$, and the
thermal conductivity, $\kappa = \rho \chi$, are both uniform throughout the domain.
The diffusivities
$\nu$ and $\chi$ therefore scale inversely with the density.

@@

\subsection{Solution for thermal evolution in a Polytrope}
Here we take the general theory described in Eqn.~\ref{eqn:general_theory} and apply it
to the specific case of the polytropes we study here. 
We note that, $\rho_0 = T_0^{m_{ad}}$ and
$dT_0 = (\grad_{\text{ad}}) dz$, such that we must solve
\begin{equation}
T_0^{-m_{ad}/2} dT_0 
= \left(\frac{\pi^{3/2}\Gamma\grad_{\text{ad}}}{V_0}\right)
\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
\label{eqn:general_theory}
\end{equation}
Assuming that $m_{ad} < 2$ and through the use of simple power law integrals, we
find that
\begin{equation}
T_0(t) = \left(C[\xi(\tau) - \xi(\tau_0)] + T_0(t_0)^{1/\alpha}  \right)^{\alpha},
\end{equation}
with
\begin{equation}
\xi(\tau) = \beta\Gamma\tau^{1/2} - (M_0 - \beta I_0) \tau^{-1/2},
\end{equation}
$C \equiv (2 \pi^{3/2} \Gamma (\grad_{\text{ad}}))/(\alpha V_0 B)$

@@

\begin{deluxetable*}{c c c c c c}
\tabletypesize{\footnotesize}
\caption{Table of simulation information
\label{table:simulation_info}
}
\tablehead{																																															
\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
\startdata																																															
\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
0.1 	& 					&	128			& 512			& 45 	&	100	\\
0.5 	& 					&	128			& 512			& 45 	&	100	\\
1	 	& 					&	128			& 512			& 45 	&	100	\\
2	 	& 					&	256			& 512			& 30 	&	100	\\
3	 	& 					&	512			& 1024			& 30 	&	100	\\
4	 	& 					&	1024		& 1024			& 30 	&	100	\\
5	 	& 					&			& 			&  	&		\\
6	 	& 					&			& 			&  	&		\\
7	 	& 					&			& 			&  	&		\\
\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
0.5 	& 					&	256			& 512			& 45 	&	0.6	\\
1	 	& 					&	256			& 512			& 45 	&	0.6	\\
2	 	& 					&	256			& 1024			& 45 	&	0.6	\\
3	 	& 					&	256			& 2048			& 45 	&	0.6	\\
\enddata																																															
\tablecomments{
}
\end{deluxetable*}

>>>>

\begin{figure}[t!]
    \includegraphics[width=\columnwidth]{evolution_colormeshes.png}
    \caption{
    \label{fig:evolution_colormeshes} }
\end{figure}

\subsection{Theoretical description of thermal evolution}
The evolution of thermals as buoyant vortex rings has been well described in
the unstratified, Boussinesq limit for decades (as early as e.g., CITE, and
see \citet{lecoanet&jeevanjee2018} for other sources). Buoyant motions 
in the atmospheres of stars and planets are generally large enough to feel the
atmospheric stratification, and therefore a more thorough treatment of the
evolution of thermals in stratified domains is required to understand 
thermal entrainment in nature.

In this work, we focus on the non-dissipative, low Mach number regime, 
in which the ideal anelastic equations are a decent approximation to the fully
compressible equations. In this regime, buoyant forces can be expressed explicitly
in terms of the entropy. In the the limit where diffusivities
are sufficiently small and therea re no thermal sources or sinks, 
the volume-integrated total entropy inside of a buoyant vortex ring is constant,
\begin{equation}
B \equiv \int_{\mathcal{V}} \rho\, s\, dV = \text{const},
\end{equation}
where $s = c_V \ln T - R \ln\rho$ is the specific entropy, with $c_V$ the
specific heat at constant volume and $R$ the ideal gas constant.

In a stratified domain, the hydrodynamic impulse is defined
\citep{shivamoggi2010},
\begin{equation}
\bm{I} = \frac{1}{2}\int_{\mathcal{V}} \bm{x}\times(\grad\times(\rho\bm{u}))dV,
\end{equation}
where $\bm{x}$ is the position vector, $\bm{u}$ is vector velocity, $\rho$ is density,
and $\mathcal{V}$ is the volume being integrated over. Impulse is equivalent to the time-integrated
work acting on the fluid resulting in the current fluid motion. 
Changes in the impulse can be expressed as
\begin{equation}
\frac{\partial\bm{I}}{\partial t} = \int_{\mathcal{V}}\frac{\partial}{\partial t}(\rho \bm{u})dV
= B\hat{z} + S,
\end{equation}
where $S$ is a combination of surface terms that disappears upon appropriate boundary conditions
on $\mathcal{V}$ \citep{shivamoggi2010}. In this context where buoyancy is the only source of
work and the buoyancy, $B$, is constant, the impulse can be straightforwardly integrated as
\begin{equation}
I_z = B t + I_0,
\end{equation}
for some constant $I_0$. In the limiting regime where all of the buoyant fluid initially
located in the thermal remains in the buoyant vortex ring, $I_0 \rightarrow 0$, but as
some of the buoyant fluid is generally detrained in the initial spin-up to a vortex ring,
it is important to keep the factor of $I_0$.
Under the assumption that the thermal develops into a thin-core 
propagating vortex ring whose vortex core is radius $r$ away from the axis of symmetry, 
the impulse can be well approximated as $I_z \approx \pi \rho r^2 \Gamma$, where 
$\Gamma = \iint (\grad\times\bm{u}) dr dz$ is the circulation in the vortex ring.
Under this approximation, it becomes clear that so long as the vortex core is bounded
by $\mathcal{V}$, the volume integrated over is rather arbitrary, as most of the circulation
is located in the concentrated vortex ring.

The vertical momentum of the thermal is less straightforward to find than the momentum. 
Upon weighting the momentum equation (Eqn.~\ref{eqn:AN_momentum_full}) by the density, 
Assuming an adiabatically stratified atmosphere in
hydrostatic equilibrium, the change in volume integrated momentum over time is
\begin{equation}
\frac{D \bm{P}}{Dt} = \frac{D}{Dt}\int_{\mathcal{V}}\rho\bm{u} dV
= \int_{\mathcal{V}} \rho\frac{D\bm{u}}{Dt} dV
\approx B\hat{z} - \int_{\mathcal{V}} \rho\grad\varpi dV.
\end{equation}
As noted by \citet{tarshish&all2018}, only infinitesimally small buoyant regions of
fluid accelerate according exactly according to their buoyant nature. Any buoyant anomaly
with a finite size disrupts its fluid environment, and this disruption results in
pressure terms which reduce the efficacy of the buoyant fluid in driving motions. 
In their work with Boussinesq thermals, they find that the true buoyant acceleration
can be well approximated by scaling down the buoyant force by a factor of O($1/2$).
Taking their work into account, we assume that the vertical momentum of the thermal
follows
\begin{equation}
P_z = \beta B t + P_0,
\end{equation}
where in this work we set $\beta = 1/2$.

Rearranging, we find our first result,
\begin{equation}
r = \sqrt{\frac{B t + I_0}{\pi\rho\Gamma}}.
\label{eqn:r_theory}
\end{equation}
In the limit where $\rho \rightarrow \text{constant}$, as in the Boussinesq regime,
we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by
\citet{lecoanet&jeevanjee2018}. We find that the inclusion of stratification adds the
additional complexity of $r \propto \rho^{-1/2}$, such that downward-propogating 
vortex rings (as studied here) will not entrain to the same degree as boussinesq thermals,
and upward-propogating rings will entrain more. In the absence of buoyancy ($B = 0$),
this result aligns with the prediction for purely horizontal compression noted by
\citet{brandenburg2016} of $r^2 \propto \rho^{-1}$.

We further assume that the volume-integrated momentum, $P_z \approx \rho V w_{th}$,
where $w_{th}$ is the vertical velocity of the thermal as a whole, and the volume
of the fluid region propogating with the thermal is a spheroid, $V = V_0 r^3$, for
some constant $V_0$. Plugging Eqn.~\ref{eqn:r_theory} into this approximation, we
find that
\begin{equation}
\rho^{-1/2}w = \left(\frac{(\pi\Gamma)^{3/2}}{V_0}\right)\frac{\beta B t + M_0}{(B t + I_0)^{3/2}}.
\end{equation}
Substituting $w = dz/dt$ and $\tau \equiv (Bt + I_0)/\Gamma$, We retrieve
\begin{equation}
\frac{dz}{\sqrt{\rho(z)}} 
= \left(\frac{\pi^{3/2}\Gamma}{V_0 B}\right)
\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
\label{eqn:general_theory}
\end{equation}
If the atmospheric stratification in which the thermal is falling is known, this
result can be straightforwardly integrated with $\rho(z)$ plugged in in order to
find the position of the thermal versus time. While we will leave this result
general for now, we will plug in our polytropic stratification at the end of
section \ref{sec:experiment}, and show that the resulting expression does a
good job of explaining the evolution of thermals in these atmospheres in
section \ref{sec:results}.

\subsection{Parameterization}

\begin{deluxetable*}{c c c c c c}
\tabletypesize{\footnotesize}
\caption{Simulation output parameterization
\label{table:simulation_info}
}
\tablehead{																																															
\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
\startdata																																															
\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
0.1 	& 					&	256			& 512			& 49 	&	0.2	\\
0.5 	& 					&	256			& 512			& 42.5 	&	0.2	\\
1	 	& 					&	256			& 512			& 38 	&	0.2	\\
2	 	& 					&	256			& 512			& 31.75	&	0.2	\\
3	 	& 					&	512			& 1024			& 27.25	&	0.2	\\
4	 	& 					&	1024		& 1024			& 25 	&	0.2	\\
5	 	& 					&			& 			&  	&		\\
6	 	& 					&			& 			&  	&		\\
7	 	& 					&			& 			&  	&		\\
\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
0.5 	& 					&	256			& 512			& 45 	&	0.2	\\
1	 	& 					&	256			& 512			& 45 	&	0.2	\\
2	 	& 					&	256			& 1024			& 45 	&	0.2	\\
3	 	& 					&	256			& 2048			& 45 	&	0.2	\\
\enddata																																															
\tablecomments{
}
\end{deluxetable*}

@@

\subsection{Anelastic Simulations}
In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic
thermals in cylindrical coordinates. 
We later verify that these simulations produce the same results a 3D fully compressible
simulations in 3D cartesian domains (see sec. REF). 
The LBR anelastic equations are \citep{lecoanet&all2014},
\begin{gather}
\td{\grad}\cdot\td{\bm{u}} = -\td{w}\partial_{\tilde{z}} \ln\rho_0 
\label{eqn:AN_continuity_full}\\
\frac{D \td{\bm{u}}}{D \td{t}} = -\td{\grad} \td{\varpi} + g\frac{\td{S_1}}{c_P}\hat{z} + \frac{1}{\rho_0}\td{\grad}\cdot\left(\mu\td{\lilstressT}\right)
\label{eqn:AN_momentum_full}\\
\frac{D \td{S_1}}{D\td{t}} = \frac{1}{\rho c_P}\td{\grad}\cdot\left(\kappa T_0 \td{\grad} \td{S_1}\right) + \frac{\mu}{\rho_0 T_0}\td{\sigma_{ij}}\partial_{\td{x_i}}\td{u_j}
\label{eqn:AN_energy_full}.
\end{gather}
where terms with tildes are dimensional, and where
$D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$. In our azimuthally symetric
domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have
no azimuthal velocity, $u_\phi$, we assume that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$. 
Under this approximation, the components of the stress tensor are
\begin{equation}
\begin{split}
&\td{\sigma}_{rr} = 2\frac{\partial \td{u_r}}{\partial \td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,
\td{\sigma}_{rz}     = \td{\sigma}_{zr} = \frac{\partial \td{w}}{\partial \td{r}} + \frac{\partial \td{u_r}}{\partial \td{z}}, \\
&\td{\sigma}_{\phi\phi} = 2\frac{\td{u_r}}{\td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,\,
\td{\sigma}_{r\phi}  = \td{\sigma}_{\phi r}  = 0, \\
&\td{\sigma}_{zz}       = 2\frac{\partial \td{w}}{\partial \td{z}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}}, \,\,\,\,\,\,
\td{\sigma}_{\phi z} = \td{\sigma}_{z \phi}  = 0,\qquad
\end{split}
\end{equation}
Furthermore, we assume that the dynamic viscosity, $\mu = \rho \nu$, and the
thermal conductivity, $\kappa = \rho \chi$, are both uniform throughout the domain.
The diffusivities
$\nu$ and $\chi$ therefore scale inversely with the density.

@@

\subsection{Solution for thermal evolution in a Polytrope}
Here we take the general theory described in Eqn.~\ref{eqn:general_theory} and apply it
to the specific case of the polytropes we study here. 
We note that, $\rho_0 = T_0^{m_{ad}}$ and
$dT_0 = (\grad_{\text{ad}}) dz$, such that we must solve
\begin{equation}
T_0^{-m_{ad}/2} dT_0 
= \left(\frac{\pi^{3/2}\Gamma\grad_{\text{ad}}}{V_0 B}\right)
\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
\label{eqn:general_theory}
\end{equation}
Assuming that $m_{ad} < 2$ and through the use of simple power law integrals, we
find that
\begin{equation}
T_0(t) = \left(C[\xi(\tau) - \xi(\tau_0)] + T_0(t_0)^{1/\alpha}  \right)^{\alpha},
\end{equation}
with
\begin{equation}
\xi(\tau) = \beta\Gamma\tau^{1/2} - (M_0 - \beta I_0) \tau^{-1/2},
\end{equation}
$C \equiv (2 \pi^{3/2} \Gamma (\grad_{\text{ad}}))/(\alpha V_0 B)$

@@

\begin{deluxetable*}{c c c c c c}
\tabletypesize{\footnotesize}
\caption{Table of simulation information
\label{table:simulation_info}
}
\tablehead{																																															
\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
\startdata																																															
\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
0.1 	& 					&	256			& 512			& 49 	&	0.2	\\
0.5 	& 					&	256			& 512			& 42.5 	&	0.2	\\
1	 	& 					&	256			& 512			& 38 	&	0.2	\\
2	 	& 					&	256			& 512			& 31.75	&	0.2	\\
3	 	& 					&	512			& 1024			& 27.25	&	0.2	\\
4	 	& 					&	1024		& 1024			& 25 	&	0.2	\\
5	 	& 					&			& 			&  	&		\\
6	 	& 					&			& 			&  	&		\\
7	 	& 					&			& 			&  	&		\\
\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
0.5 	& 					&	256			& 512			& 45 	&	0.2	\\
1	 	& 					&	256			& 512			& 45 	&	0.2	\\
2	 	& 					&	256			& 1024			& 45 	&	0.2	\\
3	 	& 					&	256			& 2048			& 45 	&	0.2	\\
\enddata																																															
\tablecomments{
}
\end{deluxetable*}
